additional charts

### 2025-04-24 report_additionalCharts.Rmd
update limVRE setup and general cleanup

# Emission reduction {.tabset}

## Gross

<!-- (c) Breakdown of residual CO2 emissions from energy and industrial processes (% in relation to 2020) -->

vars <- list(
  "Industrial\nProcesses" = "Emi|GHG|Industrial Processes",
  "Industry" = "Emi|GHG|Gross|Energy|Demand|Industry",
  "Buildings" ="Emi|GHG|Energy|Demand|Buildings",
  "Transportation" ="Emi|GHG|Energy|Demand|Transport",
  "Bunkers" = "Emi|CO2|Energy|Demand|Transport|International Bunkers",
#  "CDR" = "Emi|GHG|Gross|Energy|Demand|CDR",
#  "AFOFI" = "Emissions|CO2|Energy|Demand|AFOFI",
#  "Other Sector" ="Emissions|CO2|Energy|Demand|Other Sector",
  "Heat"="Emi|CO2|Gross|Energy|Supply|Heat",
  "Other Energy\nConversion" = "Emi|CO2|Gross|Other Energy Conversion",
    #"Hydrogen" ="Emi|CO2|Gross|Energy|Supply|Hydrogen",
    #"Liquids"="Emi|CO2|Gross|Energy|Supply|Liquids",
    #"Gases"="Emi|CO2|Gross|Energy|Supply|Gases",
    #"Solids"="Emi|CO2|Gross|Energy|Supply|Solids",
#  "Other"="Emissions|CO2|Energy|Supply|Other",
  "Electricity"="Emi|GHG|Gross|Energy|Supply|Electricity"
)
# "Emi|GHG|Agriculture",
#   "Emi|GHG|Land-Use Change",
#   "Emi|GHG|Waste",
#   "Emi|CO2|CDR|BECCS",
#   "Emi|CO2|CDR|Industry CCS|Synthetic Fuels",
#   "Emi|CO2|CDR|DACCS",
#   "Emi|CO2|CDR|EW"

plotColor <- c(
  "Electricity"= "#ffb200",
  "Heat"= "#cc0000",
  "Other Energy\nConversion" = "#0000cc",
  #"Gases"= "#999959",
  #"Liquids"= "#0000cc",
  #"Solids"= "#0c0c0c",
  #"Other" = "#79a6d2",
  #"Hydrogen" = "#5ed5b0",
  "Transportation" = "#a1dd70",
  "Bunkers" = "#ffc0cb",
  "Buildings" = "#5edfff",
  "Other Sector" = "#999959",
  "AFOFI" = "#005900",
  "Industry" = "#5f6769",
  "Industrial\nProcesses" = "#5c5c5c",
  "Other" = "#5b0d8f",
  "Waste" = "#A52A2A",
  "AFOLU" = "#4DAF4A",
  "Agriculture" = "#357933",
  "LULUCF" = "#6ec16b"
)

labels <- setNames(names(vars),vars[names(vars)])

fulldata <- df %>%
  filter(region == "EU27",
         period %in% c(2020,2030,2040),
         tgt2030 %in% tgt2030Scen,
         variable %in% unlist(vars)) %>%
  mutate(labels = factor(labels[as.character(variable)],levels = names(vars)),
         variable = factor(variable, levels = vars)) %>%
  group_by(period,variable) %>%
  mutate(min = min(value),
         max = max(value))

plotData <- fulldata %>%
  filter(scenario == mainScen) %>%
  mutate(complement = FALSE) %>%
  group_by(variable) %>%
  mutate(pct = paste0(round(value / value[period==2020],2)*100, "%")) %>%
  bind_rows(
    fulldata %>%
      filter(scenario == mainScen) %>%
      mutate(complement = TRUE) %>%
      group_by(variable) %>%
      mutate(value = value[period==2020] - value) %>%
      mutate(labels=NA)
  ) %>%
  mutate(ext_Var = ifelse(complement, paste0(as.character(variable),"_"), as.character(variable))) %>%
  arrange(period,ext_Var) %>%
  group_by(period) %>%
  arrange(variable) %>%
  mutate(ymid = as.numeric(sub("\\D+", "", period)),
         ymax = ymid + 4, ymin = ymid - 4,
         xmin = c(0, head(cumsum(value), -1)),
         xmax = cumsum(value),
         xmid = (xmax + xmin) / 2,
         ) %>%
  ungroup() %>%
  filter(complement == FALSE)

g[["2040 Emissions - Energy and Industrial Processes - Gross"]] <- plotData %>% 
  ggplot(aes(xmid, ymid, fill = ext_Var)) +
  geom_rect(aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax,
                alpha = factor(period), color = variable)) +
  geom_errorbar(data=plotData %>% filter(period == 2040), aes(xmin=xmax-value+min, xmax=xmax-value+max), width=4, colour="black", alpha=0.9, linewidth=0.8) +
  geom_text(data=plotData %>% filter(period == 2020), aes(y = 2015, label = labels, group = labels, hjust=1, angle = 90), vjust=0.5, hjust=1.1, na.rm=TRUE, size = geomText.size, angle = 90, lineheight = 0.8) +
  geom_text(data=plotData %>% filter(period == 2040), aes(x=xmid , y = 2045, label = pct), vjust=0.5, hjust=-0.1, na.rm=TRUE, size = geomText.size, angle = 90) +
  scale_fill_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) + 
  scale_alpha_manual(values = c(0.2, 0.3, 1)) +
  scale_color_manual(values = c(setNames(plotColor[names(vars)],vars)), labels = setNames(names(vars), vars)) +
  theme_doubleColumn() +
  theme(legend.position = "none") +
  scale_y_continuous(breaks=c(2020,2030,2040), labels=c("current",2030,2040), minor_breaks = NULL, limits=c(2008,2047)) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank()) +
  scale_x_continuous(breaks = NULL) +
  coord_cartesian(clip="off") +
  theme(plot.margin = margin(t = 30, r = 0, b = 100, l = 0, unit = "pt")) +
  labs(title = "(c) Sectoral breakdown of residual gross CO2 emissions from energy and industrial processes (% of average 2018-2022)") + 
  theme(plot.title = element_text(margin=margin(t=0,r=0,b=35,l=-200), hjust=1))

# ggsave(paste0(outChartsFolder,"/svg/Figure 1. Emission results panel - (c) Energy and Industrial Processes.svg"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="svg", width = 12, height = 3.2, dpi=100, units = "in")
# ggsave(paste0(outChartsFolder,"/png/Figure 1. Emission results panel - (c) Energy and Industrial Processes.png"), g[["2040 Emissions - Energy and Industrial Processes - horizontal bar"]] , device="png", width = 12, height = 3.2, dpi=300, units = "in")

@@

## Reduction Matrix
reductionMatrix <- df_beforeFilter %>% 
  filter(region == "EU27", 
         period == 2040, 
         tgt2030 == "57",
         !grepl("eedEff|ff55Eff|RpEUEff",scenario)) %>% 
  calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = round((1 - (value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))*100 ,2)) %>%
  select(bioLim,lim,reduction) %>%
  pivot_wider(names_from=lim,values_from=reduction) %>%
  mutate(bioLim = factor(c("BioLim4","BioLim7.5","BioLim12","BioLim20")))

@@

redMatrix2 <- df_beforeFilter %>%
    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
  mutate(text = paste0(round(tgtAchieved,2), "%"))

@@

plotData <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  mutate(text = paste0("Target Achieved: ", tgtAchieved, " % reduction", "\n2030 price: ", round(price_2030,2), " €/t CO2", "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim))

@@

nonAchieved2030 <- left_join(
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df_beforeFilter %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  filter(diff >= 0.5 | diff <= -0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

@@

plotData <- df_beforeFilter %>%
  filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)),
         tgtAchieved = (1-reduction)*100) %>% 
  mutate(min = min(value),
         max = max(value))

@@

nonAchieved2050 <- df_beforeFilter %>%
  filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)),
         tgtAchieved = (1-reduction)*100) %>%
  filter(tgtAchieved >= 100.3 | tgtAchieved <= 99.7) %>%
  select(scenario, reduction, tgtAchieved) %>%
  arrange(desc(abs(reduction)))

@@

fullPlotData <- df_beforeFilter %>%
  filter(region == "EU27", period %in% c(2010:2050), variable %in% unlist(vars)) %>%
  mutate(sector = factor(unlist(regmatches(variable, gregexpr('Transport|Industry|Buildings', variable))),levels=c("Industry", "Buildings", "Transport")),
         carrier= factor(unlist(regmatches(variable, gregexpr('Liquids|Gases|Solids', variable))),levels=c("Liquids", "Gases", "Solids")),
         type   = factor(unlist(regmatches(variable, gregexpr('Biomass|Hydrogen|Fossil', variable))),levels=c("Biomass", "Fossil", "Hydrogen")))

@@

<!-- <!-- # GHG Emissions --> -->

<!-- ```{r chart_, echo=FALSE, include=FALSE} -->

<!-- library(plotly) -->
<!-- plotData <- df %>%  -->
<!--   filter(region == "EU27", period %in% c(2020:2060), tgt2030 %in% tgt2030Scen) %>%  -->
<!--   calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>% -->
<!--   mutate(reduction = round((1 - (value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference))) ,2)) -->

<!-- g[["GHG emi_plotly"]] <- ggplotly(ggplot(plotData, aes(x=period,y=reduction, color=scenario)) + -->
<!--            geom_line() + -->
<!--            guides(color="none") + -->
<!--            theme_doubleColumn() + -->
<!--            scale_y_continuous(labels = scales::percent, trans="reverse") + -->
<!--            theme(axis.title.y=element_blank()) -->
<!--   ) -->

<!-- g[["GHG emi_plotly_limit"]] <- ggplotly(ggplot(plotData %>% filter(!grepl("limVRE|bio20|Nzero_55", scenario)), aes(x=period,y=reduction, color=scenario)) + -->
<!--            geom_line() + -->
<!--            guides(color="none") + -->
<!--            theme_doubleColumn() + -->
<!--            scale_y_continuous(labels = scales::percent, trans="reverse") + -->
<!--            theme(axis.title.y=element_blank()) -->
<!--   ) -->
<!-- #min(plotData %>% filter(!grepl("limVRE|bio20|Nzero_55", scenario), period == 2040) %>% pull(reduction)) -->
<!-- ``` -->

<!-- <!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} --> -->

<!-- <!-- g[["GHG emi_plotly"]] --> -->

<!-- <!-- ``` --> -->

<!-- # Electricity Capacity -->

<!-- <!-- Electricity Capacity (%) --> -->

<!-- ```{r, echo=FALSE} -->

<!-- vars <- c( -->
<!-- #  "Net Imports" = "Cap|Electricity|Imports", -->
<!--   "Coal w/ CC" = "Cap|Electricity|Coal|w/ CC", -->
<!--   "Coal w/o CC" = "Cap|Electricity|Coal|w/o CC", -->
<!--   "Oil" = "Cap|Electricity|Oil", -->
<!--   "Gas w/ CC" = "Cap|Electricity|Gas|w/ CC", -->
<!--   "Gas w/o CC" = "Cap|Electricity|Gas|w/o CC", -->
<!--   "Hydrogen" = "Cap|Electricity|Hydrogen", -->
<!--   "Nuclear" = "Cap|Electricity|Nuclear", -->
<!--   "Geothermal" = "Cap|Electricity|Geothermal", -->
<!--   "Hydro" = "Cap|Electricity|Hydro", -->
<!--   "Biomass w/ CC" = "Cap|Electricity|Biomass|w/ CC", -->
<!--   "Biomass w/o CC" = "Cap|Electricity|Biomass|w/o CC", -->
<!--   "Solar CSP" = "Cap|Electricity|Solar|CSP", -->
<!--   "Solar PV" = "Cap|Electricity|Solar|PV", -->
<!--   "Wind Onshore" = "Cap|Electricity|Wind|Onshore", -->
<!--   "Wind Offshore" = "Cap|Electricity|Wind|Offshore", -->
<!--   "Storage Battery" = "Cap|Electricity|Storage|Battery" -->
<!--   ) -->

<!-- inv_vars <- setNames(names(vars),vars) -->

<!-- color <- c( -->
<!-- #  "Net Imports"   = "#472b62", -->
<!--   "Coal w/ CC"    = "#b2b2b2", -->
<!--   "Coal w/o CC"   = "#0c0c0c", -->
<!--   "Oil"           = "#b30000", -->
<!--   "Gas w/ CC"     = "#b79e38", -->
<!--   "Gas w/o CC"    = "#999959", -->
<!--   "Hydrogen"      = "#5ed5b0", -->
<!--   "Nuclear"       = "#ff33ff", -->
<!--   "Geothermal"    = "#e51900", -->
<!--   "Hydro"         = "#191999", -->
<!--   "Biomass w/ CC" = "#33ff00", -->
<!--   "Biomass w/o CC"= "#005900", -->
<!--   "Solar CSP"     = "#ffcc00", -->
<!--   "Solar PV"      = "#ffe600", -->
<!--   "Wind Onshore"  = "#193F7F", -->
<!--   "Wind Offshore" = "#337fff", -->
<!--   "Storage Battery" = "#472b62") -->

<!-- plotData <- df %>%  -->
<!--   filter(region == "EU27", period >= 2020, period <= 2060, scenario  == mainScen, variable %in% unlist(vars)) %>%  -->
<!--   mutate(variable = factor(variable, levels=vars)) %>%  -->
<!--   arrange(factor(variable, levels = rev(vars))) %>% -->
<!--   group_by(model,scenario,region,period) %>% -->
<!--   mutate(cumValue = cumsum(value), -->
<!--          n = sum(value), -->
<!--          percentage = value / n, -->
<!--          cumPercentage = cumValue / n)  -->

<!-- plotData2040 <- plotData[plotData$period == 2040,] -->
<!-- #plotData$value <- plotData$value / plotData[plotData$period == "2020",]$value -->
<!-- #plotData$period <- as.character(plotData$period) -->
<!-- #plotData$period <- factor(plotData$period , levels = rev(c("2020","2030","2040","2050"))) -->

<!-- plotData2040$xPos <- 2042.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Hydro"),]$xPos <- 2028.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Biomass|w/o CC"),]$xPos <- 2020 -->
<!-- plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->

<!-- plotDataRenewables <- plotData %>% -->
<!--   filter(variable %in% c("Cap|Electricity|Hydrogen","Cap|Electricity|Geothermal","Cap|Electricity|Hydro","Cap|Electricity|Biomass|w/ CC","Cap|Electricity|Biomass|w/o CC","Cap|Electricity|Solar|CSP","Cap|Electricity|Solar|PV","Cap|Electricity|Wind|Onshore","Cap|Electricity|Wind|Offshore","Cap|Electricity|Nuclear","Cap|Electricity|Storage|Battery")) %>% -->
<!--   group_by(model,scenario,region,period) %>% -->
<!--   summarize(percentage = sum(percentage),.groups = "keep") -->

<!-- g[["Electricity Capacity"]] <-  -->
<!--   ggplot(plotData,aes(x=period,y=percentage)) + -->
<!--   geom_area(aes(fill=variable),alpha=0.4) + -->
<!--   geom_line(data=plotDataRenewables, linetype = "dashed", linewidth = 1.5, color="#666666") + -->
<!--   geom_bar(data=plotData2040,aes(fill=variable),stat='identity', show.legend = FALSE, alpha = 0.7, color="white", width = 3, linewidth = 1.5) + -->
<!--   #ggrepel::geom_text_repel(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(round(percentage,2)*100,"%"), y=cumPercentage-percentage/2, x = 2043.5), vjust=0.5, hjust=0.5, na.rm=TRUE, color = "black", size = 12) + -->
<!--   #geom_text(data=plotData2040[plotData2040$percentage >= 0.01,],aes(label = paste0(inv_vars[variable], " (",round(percentage,2)*100,"%)"), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size = 12) + -->
<!--   geom_text(data=plotData2040[plotData2040$percentage >= 0.02,],aes(label = paste0(round(percentage,2)*100,"%", ifelse(inv_vars[variable] %in% c("Solar PV","Wind Onshore","Wind Offshore"),paste0(" - ", inv_vars[variable]), "")), y=cumPercentage-percentage/2, x = xPos), vjust=0.5, hjust=0, na.rm=TRUE, color = "black", size=geom.text.double.size) + -->
<!--   theme_doubleColumn()  + -->
<!--   scale_y_continuous(minor_breaks = seq(0.2, 0.8, 0.2), breaks=c(0,1),labels = scales::percent) + -->
<!--   scale_x_continuous(breaks=c(2020,2040,2060)) + -->
<!--   scale_fill_manual(values = setNames(color[names(vars)],vars), labels = setNames(names(vars), vars)) + -->
<!--   theme(axis.title.y=element_blank()) + -->
<!--   guides(fill=guide_legend(nrow=8,override.aes = list(alpha=1), byrow = TRUE)) + -->
<!--   #annotate(geom = "text", x = 2022, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage + 0.06, label = "renewables", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2023, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage - 0.06, label = "and nuclear", color = "#888888",angle = 28, hjust=0, vjust=-0.5, size = 12) + -->
<!--   #annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "renewables\nand nuclear", color = "#666666",angle = 26, hjust=0, vjust=1, size=geom.text.double.size) + -->
<!--   annotate(geom = "text", x = 2020, y = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, label = "renewables,\nnuclear and hydrogen", color = "#666666",angle = 90, hjust=0.5, vjust=-0.5, size=geom.text.double.size, lineheight = 0.8) + -->
<!--   annotate(geom = "text", x = 2020, y = (1-plotDataRenewables[plotDataRenewables$period == 2020,]$percentage)/2+plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, label = "fossil", color = "#666666",angle = 90, hjust=0.5, vjust=-2, size=geom.text.double.size) + -->
<!--   annotation_custom(grob = linesGrob(gp=gpar(col="#666666",lwd = 3,lty="dashed")), xmin = 2016, xmax = 2019.8, ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage) + -->
<!--   theme(axis.text.y=element_blank()) + -->
<!--   theme(legend.key.height = unit(0.8, "cm"), -->
<!--     legend.key.width = unit(0.8,"cm")) + -->
<!--   theme(legend.spacing.y = unit(0.1, 'cm')) + -->
<!--   theme() + -->
<!--   annotate(geom = "text", label = "100%", x = 2020, y = 1, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   annotate(geom = "text", label = "0%", x = 2020, y = 0, hjust=1.2, color = "#666666", size=geom.text.double.size) + -->
<!--   coord_cartesian(clip = 'off') + -->
<!--   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 20, unit = "pt") -->
<!--         #,legend.margin=margin(l = -2, unit='cm') -->
<!--         ) #+ -->
<!--   #annotation_custom( -->
<!--   #  grob = textGrob(label = "renewables\nand nuclear",hjust=0.5, vjust=-0.5, rot = 90, gp=gpar(col="#666666", fontsize=geom.text.double.size)), -->
<!--   #  ymin = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, ymax = plotDataRenewables[plotDataRenewables$period == 2020,]$percentage/2, -->
<!--   #  xmin = 2020, xmax = 2020) -->

<!-- ggsave(paste0(outChartsFolder,"/svg/Electricity Capacity.svg"), g[["Electricity Capacity"]] , device="svg", width = 6, height = 10, dpi=100, units = "in") -->
<!-- ggsave(paste0(outChartsFolder,"/png/Electricity Capacity.png"), g[["Electricity Capacity"]] , device="png", width = 6, height = 10, dpi=300, units = "in") -->

<!-- ``` -->

<!-- ```{r, echo=FALSE, fig.width=6, fig.height=10} -->

<!-- g[["Electricity Capacity"]] -->

<!-- ``` -->

<!-- --- -->

<!-- # Electricity flexible Capacity -->

<!-- <!-- Electricity flexible Capacity (GW) --> -->

<!-- ```{r, echo=FALSE} -->

<!-- vars <- list( -->
<!--   "Variable Renewables" = c( -->
<!--     "Cap|Electricity|Solar|CSP", "Cap|Electricity|Solar|PV", "Cap|Electricity|Wind|Onshore", "Cap|Electricity|Wind|Offshore" -->

<!--   ), -->
<!--   "Hydrogen and batteries" = c( -->
<!--     "Cap|Electricity|Hydrogen","Cap|Electricity|Storage|Battery" -->

<!--   ), -->
<!--   "Dispatchable fossil" = c( -->
<!--     "Cap|Electricity|Coal|w/ CC", "Cap|Electricity|Coal|w/o CC", "Cap|Electricity|Oil", "Cap|Electricity|Gas|w/ CC", "Cap|Electricity|Gas|w/o CC" -->
<!--   ), -->
<!--   "Other non dispatchable" = c("Cap|Electricity|Nuclear", "Cap|Electricity|Geothermal", "Cap|Electricity|Hydro", "Cap|Electricity|Biomass|w/ CC", "Cap|Electricity|Biomass|w/o CC" -->
<!--   ) -->
<!-- ) -->

<!-- plotData <- NULL -->
<!-- for(group in names(vars)){ -->
<!--   plotData <- rbind( -->
<!--     plotData, -->
<!--     df %>%  -->
<!--       filter(region == "EU27",  -->
<!--              period >= 2020, period <= 2060,  -->
<!--              scenario  == mainScen,  -->
<!--              variable %in% unlist(vars[[group]])) %>% -->
<!--       group_by(model,scenario,region,period) %>% -->
<!--       summarize(value = sum(value),.groups = "keep") %>% -->
<!--       mutate(variable = group) -->
<!--     ) -->
<!--   } -->

<!-- plotData <- plotData %>% -->
<!--    mutate(variable = factor(variable, levels=names(vars))) %>%  -->
<!--    arrange(factor(variable, levels = names(vars)))  -->

<!-- # plotData <- plotData %>% -->
<!-- #   mutate(variable = factor(variable, levels=names(vars))) %>%  -->
<!-- #   arrange(factor(variable, levels = names(vars))) %>% -->
<!-- #   group_by(model,scenario,region,period) %>% -->
<!-- #   mutate(cumValue = cumsum(value), -->
<!-- #          n = sum(value), -->
<!-- #          percentage = value / n, -->
<!-- #          cumPercentage = cumValue / n)  -->

<!-- #inv_vars <- setNames(names(vars),vars) -->

<!-- color <- c( -->
<!--   "Variable Renewables"       = "#003b6d", -->
<!--   "Hydrogen and batteries"   = "#6699cc", -->
<!--   "Dispatchable fossil"   = "#bdbdbd", -->
<!--   "Other non dispatchable"    = "#676767") -->

<!-- #plotData2040 <- plotData[plotData$period == 2040,] -->
<!-- #  -->
<!-- #plotData2040$xPos <- 2042.5 -->
<!-- #plotData2040[plotData2040$variable %in% c("SE|Electricity|Nuclear","SE|Electricity|Biomass|w/o CC"),]$xPos <- 2035 -->
<!-- #  -->
<!-- # plotDataRenewables <- plotData %>% -->
<!-- #   filter(variable %in% c("Cap|Electricity|Hydrogen","Cap|Electricity|Geothermal","Cap|Electricity|Hydro","Cap|Electricity|Biomass|w/ CC","Cap|Electricity|Biomass|w/o CC","Cap|Electricity|Solar|CSP","Cap|Electricity|Solar|PV","Cap|Electricity|Wind|Onshore","Cap|Electricity|Wind|Offshore","Cap|Electricity|Nuclear","Cap|Electricity|Storage|Battery")) %>% -->
<!-- #   group_by(model,scenario,region,period) %>% -->
<!-- #   summarize(percentage = sum(percentage),.groups = "keep") -->

<!-- g[["Electricity flexible capacity"]] <-  -->
<!--   ggplot(plotData,aes(x=period,y=value)) + -->
<!--   geom_area(aes(fill=variable), alpha = 0.9) + -->

>>>>

@@

## Reduction Matrix
reductionMatrix <- df %>% 
  filter(region == "EU27", 
         period == 2040, 
         tgt2030 == "57",
         !grepl("eedEff|ff55Eff|RpEUEff",scenario)) %>% 
  calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = round((1 - (value / tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)))*100 ,2)) %>%
  select(bioLim,lim,reduction) %>%
  pivot_wider(names_from=lim,values_from=reduction) %>%
  mutate(bioLim = factor(c("BioLim4","BioLim7.5","BioLim12","BioLim20")))

@@

redMatrix2 <- df %>%
    filter(region == "EU27", period == 2040, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
  mutate(text = paste0(round(tgtAchieved,2), "%"))

@@

plotData <- left_join(
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  mutate(text = paste0("Target Achieved: ", tgtAchieved, " % reduction", "\n2030 price: ", round(price_2030,2), " €/t CO2", "\nScenario: ", scenario, "\nTarget 2030: ", tgt2030, "%", "\nEfficiency: ", efficiency, "\nBiomass Limit: ", bioLim, "\nSensititivy limit: ", lim))

@@

nonAchieved2030 <- left_join(
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen) %>%
    calc_addVariable( "`Emissions with LULUCF and with intra-EU aviation`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers|Intra-region`" , units = "Mt CO2/yr", only.new=T) %>%
    mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with intra-EU aviation") %>% pull(reference)),
           tgtAchieved = (1-reduction)*100,
           diff = as.numeric(as.character(tgt2030)) - ((1-reduction)*100)) %>%
    group_by(tgt2030) %>% 
    mutate(min = min(value),
           max = max(value)),
  df %>%
    filter(region == "EU27", period == 2030, tgt2030 %in% tgt2030Scen, variable == "Price|Carbon") %>%
    mutate(price_2030 = currencyConversion*value) %>%
    select(scenario, price_2030),
  by = "scenario") %>%
  filter(diff >= 0.5 | diff <= -0.5) %>%
  select(scenario, price_2030, tgt2030, tgtAchieved, diff) %>%
  arrange(desc(abs(diff)))

@@

plotData <- df %>%
  filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)),
         tgtAchieved = (1-reduction)*100) %>% 
  mutate(min = min(value),
         max = max(value))

@@

nonAchieved2050 <- df %>%
  filter(region == "EU27", period == 2050, tgt2030 %in% tgt2030Scen) %>%
  calc_addVariable( "`Emissions with LULUCF and with international transport`" = "`Emi|GHG|LULUCF national accounting` + `Emi|CO2|Energy|Demand|Transport|International Bunkers`" , units = "Mt CO2/yr", only.new=T) %>%
  mutate(reduction = value / (tgt %>% filter(target == "Emissions with LULUCF and with international transport") %>% pull(reference)),
         tgtAchieved = (1-reduction)*100) %>%
  filter(tgtAchieved >= 100.3 | tgtAchieved <= 99.7) %>%
  select(scenario, reduction, tgtAchieved) %>%
  arrange(desc(abs(reduction)))

@@

fullPlotData <- df %>%
  filter(region == "EU27", period %in% c(2010:2050), variable %in% unlist(vars)) %>%
  mutate(sector = factor(unlist(regmatches(variable, gregexpr('Transport|Industry|Buildings', variable))),levels=c("Industry", "Buildings", "Transport")),
         carrier= factor(unlist(regmatches(variable, gregexpr('Liquids|Gases|Solids', variable))),levels=c("Liquids", "Gases", "Solids")),
         type   = factor(unlist(regmatches(variable, gregexpr('Biomass|Hydrogen|Fossil', variable))),levels=c("Biomass", "Fossil", "Hydrogen")))

@@
